Model-based variable selection for regression with highly correlated variables.

### 2014-05-15 www/article13.tex
up
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@604 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

The theorem from Maugis guarantee that a sub-regression between Gaussian mixtures is identifiable in terms of which one is regressed by others.
		\begin{eqnarray}
%			\forall j \in I_r, \boldsymbol{X}^j_{|\boldsymbol{X}^G,\boldsymbol{X}^{G^c}}&=& \boldsymbol{X}^G\boldsymbol{\alpha}_j^G+\boldsymbol{X}^{G^c}\boldsymbol{\alpha}_j^{G^c}+ \boldsymbol{\varepsilon}_j \\
%			\boldsymbol{X}^j_{|\boldsymbol{X}^{G^c}}&=& \boldsymbol{X}^{G^c}\boldsymbol{\alpha}_j^{G^c} + \tilde{\boldsymbol{\varepsilon}}_j \textrm{ is identifiable where} \\
%			\tilde{\boldsymbol{\varepsilon}}_j&=&\boldsymbol{X}^{G}\boldsymbol{\alpha}_j^{G}+ \boldsymbol{\varepsilon}_j \textrm{ is Gaussian. 
		 \boldsymbol{X}_{r|\boldsymbol{X}^G,\boldsymbol{X}^{G^c}}&=& \boldsymbol{X}^G\boldsymbol{\alpha}_G+\boldsymbol{X}^{G^c}\boldsymbol{\alpha}_{G^c}+ \boldsymbol{\varepsilon} \\
			\boldsymbol{X}_{r|\boldsymbol{X}^{G^c}}&=& \boldsymbol{X}^{G^c}\boldsymbol{\alpha}_{G^c} + \tilde{\boldsymbol{\varepsilon}} \textrm{ is identifiable where} \\
			\tilde{\boldsymbol{\varepsilon}}_j&=&\boldsymbol{X}^{G}\boldsymbol{\alpha}_j^{G}+ \boldsymbol{\varepsilon}_j \textrm{ is Gaussian.}  
		\end{eqnarray}
%		We have the unique (Gaussian are allowed only on the right of the sub-regressions) decomposition $f(\boldsymbol{X}_r|\boldsymbol{X}_f)=f(\boldsymbol{X}_r|\boldsymbol{X}^G,\boldsymbol{X}^{G^c})=f(\boldsymbol{X}_r|\boldsymbol{X}^{G^c})f(\boldsymbol{X}^{G}) $ 
%		where  $f(\boldsymbol{X}_r|\boldsymbol{X}^{G^c})$ is identifiable. Moreover, $\boldsymbol{X}^{G}$ is a set (empty or not) of independent Gaussian variables, whose parameters are identifiable.
%		So the structure is identifiable.
%		\begin{eqnarray}
%			f(\boldsymbol{X})&=&f(\boldsymbol{X}\setminus\boldsymbol{X}^{G},\boldsymbol{X}^{G})=f(\boldsymbol{X}_r|\boldsymbol{X}^{G^c},\boldsymbol{X}^{G})f(\boldsymbol{X}^{G^c},\boldsymbol{X}^{G}) \\
%			&=& f(\boldsymbol{X}_r|\boldsymbol{X}^{G^c},\boldsymbol{X}^{G})f(\boldsymbol{X}^{G^c})f(\boldsymbol{X}^{G}) \\
%		\end{eqnarray}
%		
%		\begin{equation}
%			
%		\end{equation}
	%It can also be extended to the $(S,R,U,W)$ model with variables of $\boldsymbol{X}_f$ independent from $\boldsymbol{X}_r$ defining ...
	The presence of two Gaussian mixtures on the right of the sub-regression gives the identifiability of it (even with also Gaussian variables) by the strict increase of the component number when combining Gaussian mixtures.
	So a sub-regression is identifiable if it has only Gaussian mixtures (even only one) on the right or if it has at least two Gaussian mixtures (even with additional Gaussian variables)

>>>>

The theorem from Maugis guarantee that a sub-regression between Gaussian mixtures is identifiable in terms of which one is regressed by others.
		\begin{eqnarray}
%			\forall j \in I_r, \boldsymbol{X}^j_{|\boldsymbol{X}^G,\boldsymbol{X}^{G^c}}&=& \boldsymbol{X}^G\boldsymbol{\alpha}_j^G+\boldsymbol{X}^{G^c}\boldsymbol{\alpha}_j^{G^c}+ \boldsymbol{\varepsilon}_j \\
%			\boldsymbol{X}^j_{|\boldsymbol{X}^{G^c}}&=& \boldsymbol{X}^{G^c}\boldsymbol{\alpha}_j^{G^c} + \tilde{\boldsymbol{\varepsilon}}_j \textrm{ is identifiable where} \\
%			\tilde{\boldsymbol{\varepsilon}}_j&=&\boldsymbol{X}^{G}\boldsymbol{\alpha}_j^{G}+ \boldsymbol{\varepsilon}_j \textrm{ is Gaussian. 
		 \boldsymbol{X}_{r|\boldsymbol{X}^G,\boldsymbol{X}^{G^c}}&=& \boldsymbol{X}^G\boldsymbol{\alpha}_G+\boldsymbol{X}^{G^c}\boldsymbol{\alpha}_{G^c}+ \boldsymbol{\varepsilon} \\
			\boldsymbol{X}_{r|\boldsymbol{X}^{G^c}}&=& \boldsymbol{X}^{G^c}\boldsymbol{\alpha}_{G^c} + \tilde{\boldsymbol{\varepsilon}} \textrm{ is identifiable where} \\
			\tilde{\boldsymbol{\varepsilon}}_j&=&\boldsymbol{X}^{G}\boldsymbol{\alpha}_j^{G}+ \boldsymbol{\varepsilon}_j \textrm{ is Gaussian.}  
		\end{eqnarray}
%		We have the unique (Gaussian are allowed only on the right of the sub-regressions) decomposition $f(\boldsymbol{X}_r|\boldsymbol{X}_f)=f(\boldsymbol{X}_r|\boldsymbol{X}^G,\boldsymbol{X}^{G^c})=f(\boldsymbol{X}_r|\boldsymbol{X}^{G^c})f(\boldsymbol{X}^{G}) $ 
%		where  $f(\boldsymbol{X}_r|\boldsymbol{X}^{G^c})$ is identifiable. Moreover, $\boldsymbol{X}^{G}$ is a set (empty or not) of independent Gaussian variables, whose parameters are identifiable.
%		So the structure is identifiable.
%		\begin{eqnarray}
%			f(\boldsymbol{X})&=&f(\boldsymbol{X}\setminus\boldsymbol{X}^{G},\boldsymbol{X}^{G})=f(\boldsymbol{X}_r|\boldsymbol{X}^{G^c},\boldsymbol{X}^{G})f(\boldsymbol{X}^{G^c},\boldsymbol{X}^{G}) \\
%			&=& f(\boldsymbol{X}_r|\boldsymbol{X}^{G^c},\boldsymbol{X}^{G})f(\boldsymbol{X}^{G^c})f(\boldsymbol{X}^{G}) \\
%		\end{eqnarray}
%		
%		\begin{equation}
%			
%		\end{equation}
	%It can also be extended to the $(S,R,U,W)$ model with variables of $\boldsymbol{X}_f$ independent from $\boldsymbol{X}_r$ defining ...

Here, $\otimes$ and $\oplus$ denote respectively the kronecker product and sum.
	\begin{eqnarray}
			\forall j \in I_r : \  \boldsymbol{X}^j_{|\boldsymbol{X}_f}&\sim & \mathcal{N}(\boldsymbol{X}_f\boldsymbol{\alpha}_j,\sigma^2_j\boldsymbol{I}_n) \label{densitycondgauche}\\
			\forall j \in I_f : \boldsymbol{X}^j_{|S} &\sim& \mathcal{GM}(\boldsymbol{\pi}_j;\boldsymbol{\mu}_j;\boldsymbol{\sigma}^2_j) \textrm{ with } \boldsymbol{\pi}_j,\boldsymbol{\mu}_j,\boldsymbol{\sigma}^2_j \textrm{ vectors of size } K_j  \label{densitydroite}\\
			\textrm{And we obtain, } \forall j \in I_r : \  \boldsymbol{X}^j&\sim & 
						\mathcal{GM}(\bigotimes_{\substack{i \in I_f^j  }}\boldsymbol{\pi}_i \ ; 
			                         \bigoplus_{\substack{i \in I_f^j  }} \alpha_{i,j} \boldsymbol{\mu}_i \ ; 
			                         \boldsymbol{\sigma}_j^2+\bigoplus_{\substack{i \in I_f^j  }}\alpha_{i,j}^2 \boldsymbol{\sigma}_i^2 )\label{densitygauche}          
		\end{eqnarray}
		So when we compare (\ref{densitydroite}) and (\ref{densitygauche}) we see that the number of components in $I_r$ variables differs when subregressions are of length $>1$ (almost 2 predictors) with multiple-class predictors (so the kronecker product is effective).

	The presence of two Gaussian mixtures on the right of the sub-regression gives the identifiability of it (even with also Gaussian variables) by the strict increase of the component number when combining Gaussian mixtures.
	So a sub-regression is identifiable if it has only Gaussian mixtures (even only one) on the right or if it has at least two Gaussian mixtures (even with additional Gaussian variables)
